Guaranteeing Safety and Liveness of Unmanned Aerial Vehicle Platoons on Air Highways

### 2015-11-30 docs/AIAA 2015/main.tex
updated air highways section
no message
New template for platoon paper journal version

\documentclass[letterpaper]{AIAA}

\newcommand{\hw}{\mathbb{H}}
\newcommand{\hwd}{\hat{d}}
\newcommand{\cost}[1]{c_\text{#1}}

@@

\author{Mo Chen\footnote{Insert Job Title, Department Name, Address/Mail Stop, and AIAA Member Grade (if any) for first author.}}
\affiliation{Business or Academic Affiliation 1, City, State, Zip Code}
\author{Third C. Author\footnote{Insert Job Title, Department Name, Address/Mail Stop, and AIAA Member Grade (if any) for third author.}}
\affiliation{Business or Academic Affiliation 2, City, Province, Zip Code, Country}
\author{Fourth D. Author\footnote{Insert Job Title, Department Name, Address/Mail Stop, and AIAA Member Grade (if any) for fourth author (etc.).}}
\affiliation{Business or Academic Affiliation 2, City, State, Zip Code}

\begin{abstract}
\end{abstract}

@@

\input{introduction.tex}
\input{high_form.tex}
\input{high_eikon.tex}
\input{high_sim.tex}
\input{plat_form.tex}
\input{plat_reach.tex}
\input{plat_intra.tex}
\input{plat_inter.tex}
\input{plat_safety.tex}
\input{plat_sim.tex}
\input{conclusions.tex}

>>>>

\documentclass[journal]{aiaa-pretty}

\newcommand{\hw}{\mathbb{H}}
\newcommand{\hwd}{\hat{d}}
\newcommand{\cost}[1]{c_\text{#1}}
\newcommand{\hpath}{\mathcal{P}}
\newcommand{\wpt}{\mathcal{W}}

\author{Mo Chen}

\abstract{Abstract.}

@@

@@

\input{introduction.tex}
\input{high_form.tex}
\input{high_eikon.tex}
\input{high_waypoints.tex}
\input{high_sim.tex}
\input{plat_form.tex}
\input{plat_reach.tex}
\input{plat_intra.tex}
\input{plat_inter.tex}
\input{plat_safety.tex}
\input{plat_sim.tex}
\input{conclusions.tex}
